% Cover letter using letter.sty
\documentclass{letter} % Uses 10pt
\usepackage{hyperref}
%Use \documentstyle[newcent]{letter} for New Century Schoolbook postscript font
% the following commands control the margins:
\topmargin=-1in    % Make letterhead start about 1 inch from top of page 
\textheight=8in  % text height can be bigger for a longer letter
\oddsidemargin=0pt % leftmargin is 1 inch
\textwidth=6.5in   % textwidth of 6.5in leaves 1 inch for right margin

\begin{document}

\signature{Dana A. Merrick}           % name for signature 
\longindentation=0pt                       % needed to get closing flush left
\let\raggedleft\raggedright                % needed to get date flush left
 
 
\begin{letter}{Second Dinner \\
Irvine, CA 92618}


\begin{flushleft}
{\large\bf Dana A. Merrick}
\end{flushleft}
\medskip\hrule height 1pt
\begin{flushright}
\hfill dana.merrick@gmail.com \\
\hfill (978) 206-1331
\end{flushright} 
%\vfill % forces letterhead to top of page

 
\opening{Dear Second Dinner:} 
 
\noindent I have updated my resume twice in the last year: once back in July on the day Second Dinner was announced, and again today in preparation for this application. Simply put, I can't remember the last time I have been this excited about a project.

\noindent Who am I? I'm an experienced infrastructure engineer who has worked with many small/medium teams as they grew to successful companies. I have a history of architecting infrastructures that are simple, reliable, affordable, and scalable. I also have something uncommon in my field... social skills! I enjoy working with non-technical teams, interacting with customers, and I am always pleased to find opportunities to share my knowledge with the engineering team.

\noindent When I wrote to you back in July, I was on sabbatical; I had taken a year off to travel the USA in a campervan. I have since settled back into Real Life, but I'm keeping the vanlife dream alive with a Twitch channel (available at \href{http://whereisdana.today}{whereisdana.today}). If you stop in, be sure to interact with my custom bot (source code available on my GitHub).

\noindent I appreciate your time in considering me for this role. Please do not hesitate reach out if you have any questions!

 
\closing{Sincerely yours,} 


\vfill

\begin{itemize}
	\item \href{https://github.com/dmerrick/resume}{https://github.com/dmerrick/resume}
	\item \href{https://www.linkedin.com/in/danamerrick}{https://www.linkedin.com/in/danamerrick}
	\item \href{https://dana.lol}{https://dana.lol}
	\item \href{http://whereisdana.today}{http://whereisdana.today}
\end{itemize}




% \encl{}  				% Enclosures

\end{letter}
 

\end{document}






