%
%               ________________________________________________
%              /                                                \
%             |    _________________________________________     |
%             |   |                                         |    |
%             |   |  $ cat README                           |    |
%             |   |                                         |    |
%             |   |                 Hello!                  |    |
%             |   |                                         |    |
%             |   |   This is Dana's Resume source code.    |    |
%             |   |                                         |    |
%             |   | For the human-readable version, visit:  |    |
%             |   |                                         |    |
%             |   |       github.com/dmerrick/resume        |    |
%             |   |                                         |    |
%             |   |                -Dana Merrick            |    |
%             |   |                                         |    |
%             |   |_________________________________________|    |
%             |                                                  |
%              \_________________________________________________/
%                     \___________________________________/
%                  ___________________________________________
%               _-'    .-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-.  --- `-_
%            _-'.-.-. .---.-.-.-.-.-.-.-.-.-.-.-.-.-.-.--.  .-.-.`-_
%           _-'.-.-.-. .---.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-`__`. .-.-.-.`-_
%      _-'.-.-.-.-. .-----.-.-.-.-.-.-.-.-.-.-.-.-.-.-.-----. .-.-.-.-.`-_
%   _-'.-.-.-.-.-. .---.-. .-------------------------. .-.---. .---.-.-.-.`-_
%  :-------------------------------------------------------------------------:
%  `---._.-------------------------------------------------------------._.---'

% things I could add:
% able to work across teams, across skillsets
% excellent oral/written communication and documentation skills
% sense of humor
% technology educator
% almost 100.0% uptime at Snapdocs
% visa status

% LaTeX resume using res.cls
\documentclass[line,margin]{res}

\begin{document}

\name{Dana Atchley Merrick}
% this is sloppy but its easy formatting
\address{\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\, dana.merrick@gmail.com}
\address{\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,\,USA-based -- 978.206.1331}

\begin{resume}

\section{HIGHLIGHTS}
  \begin{itemize}  \itemsep -2pt % reduce space between items
    \item Technology generalist
    \item Detail-oriented \& level-headed
    \item Motivated problem solver
    \item Superb communication skills
    \item Experience in many industries
  \end{itemize}
  
\section{EXPERIENCE}
  {\sl Senior Engineer}  \hfill 2019-present \\
  Postmates,
  San Francisco, CA
  \begin{itemize}  \itemsep -2pt % reduce space between items
    \item Lead infrastructure efforts for a startup-within-a-startup: the Postmates developer API.
    \item Built out API server functionality in Go -- including metrics, logging, tracing, and new features.
    \item Integrated Docker build process and Kubernetes deploy pipeline with existing Postmates tools.
    \item Served as liaison between developer API team and the greater Postmates infrastructure team.
  \end{itemize}

  {\sl Senior Infrastructure Engineer}  \hfill 2016-18 \\
  Snapdocs,
  San Francisco, CA
  \begin{itemize}  \itemsep -2pt % reduce space between items
    \item Full ownership of the infrastructure: security, performance, reliability, cost, architecture, testing, tooling, documentation, and more.
    \item Built a suite of internal tools to assist with development, testing, deployment, and administration.
    \item Migrated from AWS OpsWorks to Elastic Beanstalk using CloudFormation.
    \item Oversaw a SOC 2 audit.
    \item Served as a mentor/educator to entire engineering team.
  \end{itemize}

  {\sl Senior Infrastructure Engineer}  \hfill 2015-16 \\
  Plaid,
  San Francisco, CA
  \begin{itemize}  \itemsep -2pt % reduce space between items
    \item Built out a Vagrant developer environment that utilized the same Chef infrastructure code as the production environment.
    \item Designed and implemented a system to run integration testing suite against every pull request, catching many bugs before they were deployed.
    \item Created a Github Enterprise server and migrated all private repositories/users.
    \item Moved a manually-maintained Nagios alerting system to one fully automated with Chef.
    \item Built countless internal tools to assist with development, testing, and deployment.
    \item Upgraded massive production MongoDB server cluster to the latest version with zero downtime.
  \end{itemize}

  {\sl Lead Infrastructure Engineer}  \hfill 2014-15 \\
  IFTTT,
  San Francisco, CA
  \begin{itemize}  \itemsep -2pt % reduce space between items
    \item Worked as sole infrastructure engineer responsible for servers on AWS and Heroku.
    \item Prepared for and oversaw the system during the launch of the Do apps.
 
    \vspace{-2.5mm} % reduce the space before the list
    \begin{itemize}  \itemsep -3pt % reduce space between items
      \item The company's biggest launch to date.
      \item Featured eight new apps, global press coverage, and millions of new users. 
      \item The entire launch week went impeccably.
    \end{itemize}
    \vspace{-2.0mm} % reduce the space after the list

    \item Managed a sophisticated job queuing system using Resque/Redis, which directed tremendous amounts of API traffic across nearly 200 different APIs.
    \item Updated Chef infrastructure to most recent version and best practices.
    \item Cleaned up the codebase and the infrastructure from cruft, outdated/broken tools, and unnecessary costs.
    \item Countless improvements to monitoring and alerting tools, including PagerDuty, Pingdom, New Relic, Graphite, and CloudWatch.
    \item Improved stability of deploy process; reduced the total deploy time by 50\%.
    \item Dramatically reduced the frequency of incidents requiring human intervention.
    \item Contributed to many other areas of the company, including product design, marketing, community/support, and HQ operations.
  \end{itemize}

  {\sl Platform Engineer}  \hfill 2011-14 \\
  Brightcove / Zencoder,
  San Francisco, CA
  \begin{itemize}  \itemsep -2pt % reduce space between items
    \item Lead the team responsible for replacing Brightcove's transcoding stack with Zencoder infrastructure.
    \item Helped design, build, and support a platform for cross-platform mobile development.
    \item Managed build farm, Postgres/MongoDB databases, Riak servers, Nagios systems, and Resque queues.
    \item Migrated the AWS infrastructure to both Vagrant and physical servers.
    \item Personally handled many long-term operations projects:

    \vspace{-2.5mm} % reduce the space before the list
    \begin{itemize}  \itemsep -3pt % reduce space between items
      \item Built a development environment to run the AWS infrastructure code locally using Chef and Vagrant.
      \item Automated building of machine images using Packer.
      \item Modernized the Chef infrastructure using tools like Berkshelf and Foodcritic.
      \item Upgraded Ruby from Ruby Enterprise 1.8.7 to Ruby 2.1.
    \end{itemize}
  \end{itemize}

  {\sl Software Engineer}  \hfill 2010-11 \\
  BCM (formerly Backchannelmedia),
  Boston, MA
  \begin{itemize}  \itemsep -2pt % reduce space between items
    \item Lead a small team of Ruby developers in designing, building, and launching a Rails 3 daily deal site.
    \item Personally handled entire Rails deploy and release management process using Engine Yard, Heroku, and AWS.
    \item Earned a reputation as the resident Git expert; provided lessons, presentations, and advice on getting the most out of SCM in day-to-day development.
  \end{itemize}

  {\sl Web Software Developer}  \hfill 2009 \\
  Wieck Media,
  Dallas, TX
  \begin{itemize}  \itemsep -2pt % reduce space between items
    \item Pure Ruby development; contributing to the company's in-house web framework (and Rails alternative), called ``Harbor."
    \item Designed and developed libraries (gems) for user, media, and release management, including a heavy focus on i18n for an international client.
  \end{itemize}

  {\sl System Administrator}  \hfill 2006-09 \\
  Integrated Computer Solutions,
  Bedford, MA
  \begin{itemize}  \itemsep -2pt %reduce space between items
       \item Managed all physical machines, including production servers, personal work stations, virtual machines, and legacy hardware.
       \item Designed and built a custom server-monitoring system.
  \end{itemize}

\section{EDUCATION}
  {\sl Trinity College,}
  Hartford, CT \hfill 2010 \\
  Bachelor of Science, Double Major \\
  Computer Science \& Classical Mathematics \\
  Charter member: Hartford area Ruby group

\section{PORTFOLIO}
  My GitHub account has many public repositories for you to browse. \\
  The most up-to-date version of this r\'{e}sum\'{e} can also be found there. \\
  You may find it at \texttt{github.com/dmerrick}.

\section{LOOKING FOR}
  Opportunity to be rewarded for innovation and leadership. \\
  Camaraderie in an exceptional team. \\
  Adoption of modern technologies.

\section{REFERENCES}
  Available upon request.

\end{resume}
\end{document}
